Enhancement of SDR in Thessaloniki

### 2024-08-25 GHI_enh_03_process.tex
Commit 2024-06-06 20:17
Commit 2024-06-10 10:14
Commit 2024-08-24 06:14
Commit 2024-08-25 19:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-06}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
    0.0    89.7   180.0   180.0   270.3   360.0 
\end{verbatim}

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.5835   0.6886   0.3233  28.1502  83.4876 
\end{verbatim}

@@

\begin{verbatim}
aa
aatm
aday
adjpoint55
AEin1
All_daily_ratio_lim
alpha
amean
ampl
asza
atype
avar
b
BIO_ELEVA
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
fit
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
lm_mean
lm_zeropoint
mean_55
mean_BR_55
mean_BR_mean
mean_BR_median
mean_BR_min
mean_mean
mean_median
mean_min
mid
MIN_ELEVA
MIN_N
mm
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
slope_55
slope_mean
slope_median
slope_min
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
t
tsy
units
variables_fl
xlim
yearstodo
ylim
zeropoint
zeropointA
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-06-06 10:26:55.1 athan@tyler GHI_enh_03_process.R 5.853366 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-25}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   0.00   89.59  180.00  180.00  270.41  360.00 
\end{verbatim}

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.4719   0.7629   0.4279  28.2416  83.4876 
\end{verbatim}

@@

\begin{verbatim}
aa
aatm
aday
adjpoint55
AEin1
All_daily_ratio_lim
alpha
amean
ampl
asza
atype
avar
b
BIO_ELEVA
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
fit
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
lm_mean
lm_zeropoint
mean_55
mean_BR_55
mean_BR_mean
mean_BR_median
mean_BR_min
mean_mean
mean_median
mean_min
mid
MIN_ELEVA
MIN_N
mm
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
slope_55
slope_mean
slope_median
slope_min
solar_constant
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
t
tsy
units
variables_fl
xlim
yearstodo
ylim
zeropoint
zeropointA
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-08-25 15:41:24.7 athan@tyler GHI_enh_03_process.R 7.859937 mins
\end{verbatim}
